---
title: "Lab 3: Hypothesis Testing"
author: "Your Names"
date: "4/15/2021"
output: html_document
---

```{r setup, include=FALSE}
#These are global specifications for how the RMarkdown file should knit. 
#Do not change these or delete these!
knitr::opts_chunk$set(echo = TRUE, 
                      tidy = TRUE, 
                      message = FALSE, 
                      fig.align = "center")
```

```{r libraries}
#load in some packages--make sure to run this code chunk!
#if you don't have tidyverse installed, uncomment and run the next line 

#install.packages("tidyverse")
library(tidyverse)
```

First, let's load in the data. The data are stored in a .csv file, so read in the data using `read.csv()`. Don't forget to assign the data to a variable. 

__1. Load in the data in the code chunk below with `read.csv()` and name the variable `bechdel_data`.__

```{r}

```

## The Data

Today we will be exploring hypothesis testing with one-sided Z-tests using the `bechdel` dataset from fivethirtyeight. 

These data are on 1,794 movies from 1970 to 2013 with information on the year the movie was released, budget, domestic and international gross (all in 2013 dollars), and whether or not it passed the Bechdel test. The Bechdel test is a gender bias test with three extremely basic criteria to check for gender bias--in order to pass, there must be at least two named female characters, they must have a conversation with one another, and that conversation cannot be about men. A shocking number of movies fail this simple test!

This data set was collected for fivethirtyeight's article [The Dollar-And-Cents Case Against Hollywood’s Exclusion of Women](https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/), and the GitHub repo can be found [here](https://github.com/fivethirtyeight/data/tree/master/bechdel). 

To get a visual overview of the relationship between budget in 2013 dollars and domestic gross profit in 2013 dollars, and whether or not these movies passed the Bechdel test, run the code chunk below. This code is also good reference for groups last week who were interested to learn more about `tidyverse` and `ggplot`!!

```{r message=FALSE, warning=FALSE}
bechdel_data %>%
  ggplot(aes(x = budget_2013, y = domgross_2013, color = binary)) + 
  geom_point(size = 1) + 
  geom_smooth(method = "lm", se = FALSE, color = "black", size = .5) +
  scale_x_continuous(labels = scales::comma) + 
  scale_y_continuous(labels = scales::comma) + 
  labs(color = "bechdel test") +
  xlab("budget (in 2013 dollars)") +
  ylab("domestic gross (in 2013 dollars)") +
  annotate("text", x = 420000000, y = 750000000, label = "Avatar (2009)") + 
  annotate("text", x = 25339314, y = 1000038377, label = "E.T. (1982)") +
  annotate("text", x = 50000000, y = 1700000000, label = "Star Wars (1977)") + 
  annotate("text", x = 51937204, y = 1225306085, label = "Jaws (1975)") +
  annotate("text", x = 142926730, y = 1074306128, label = "The Exorcist (1973)") +
  annotate("text", x = 290247625, y = 915890356, label = "Titanic (1997)")
```

## One-way t-test 

We are going to start with a one-sided t-test to answer the question **Is the average budget for A-list movies made between 1970 and 2013 greater than $50,000,000?**.

For the purpose of this exercise, assume that the dataset is a randomly collected sample of A-list movies for this time period. 

__2. What are the null and alternative hypotheses for this test? (Hint: pay attention to the direction of your hypotheses)__
<!-- Your response here -->


Next we will need to calculate the t-statistic, which comes from this formula (mouse over the characters inside the dollar signs to view the formula) $$t = \frac{\bar{x} - \mu_0}{s/\sqrt{n}}$$

* x-bar is the sample mean
* mu_0 is the population mean from the hypotheses
* s is the sample standard deviation 
* n is the sample size 

In R, to calculate the t-stat "by hand", we use a formula like the one below, where `x` is a stand-in for data (the `budget_2013` column in this problem). 

In the example code below, I have shown how to save each value into an intermediate variable for clarity, but this is not necessary.

```{r}
n <- nrow(x) #saves the number of observations in a dataset
mean <- mean(x) #mean
sd <- sd(x) #standard deviation
mu <- NA #replace this with the population parameter from the hypotheses

t_stat <- (mean - mu) / (sd / sqrt(n))
```

__3. In the code chunk below, calculate the t-stat to test whether or not the average budget for A-list movies from 1970 to 2013 is greater than $50,000,000.__

```{r}

```

__4. What is your t-statistic?__
<!-- Your response here -->


Next, we will need to calculate the p-value for this hypothesis test. 

__5. Will this be a one-sided or two-sided p-value?__
<!-- Your response here -->


We can calculate the p-value using the `pt()` function in order to avoid needing a cdf to complete this calculation.

* the first (`q`) is where we supply the t-stat from the previous step. If you saved this number to a variable, you can supply the variable name, and if not, you can just type the number 
* the `df` arg is where we supply the degrees of freedom, which is n-1 (for this example, df = 1793)
* `lower.tail` lets us specify whether or not the p-value should come from the lower tail of the t-distribution, either TRUE or FALSE (for this exmaple, the alternative is that the average budget is greater than 50,000,000, so we will use FALSE)

__6. Fill in the rest of the code chunk below to find the p-value__

```{r}
pt(q = , 
   df = , 
   lower.tail = )
```

__7. Report your p-value below__
<!-- Your response here -->


### t-tests with `t.test()`

Luckily, we can also do this test far more easily with the `t.test()` function. 

To use this function: 
* supply the data to the `x` argument
* supply the alternative hypothesis (to learn valid arguments, search the help file by running "?t.test" in your console to view the help file)
* mu is the number indicating the population parameter (true value of the mean)

__8. Fill in the blanks in the code chunk below to complete the t-test with the `t.test()` function__ 

```{r}
t.test(x = , 
       alternative = ,
       mu = )
```

__9. Did you get the same t-stat and p-value as in the previous section?__
<!-- Your response here -->


__10. What does this p-value mean in context?__
<!-- Your response here -->


__11. Based on the p-value and t-statistic, should we reject or fail to reject the null hypothesis? Why? Remember to add context from the problem to your response.__
<!-- Your response here -->


### Two-way t-test

For the last section, we will investigate whether movies that pass the Bechdel test perform better than movies that fail the test, using a two-way t-test. The question we want to answer is: **Do movies that pass the Bechdel test make more profit that movies that don't?**

First, run this code chunk to create a data frame storing all the movies that passed the bechdel test (`bechdel_pass`) and another to store all the movies that did not pass. 

```{r}
bechdel_pass <- bechdel_clean %>% 
  filter(binary == "PASS")

bechdel_fail <- bechdel_clean %>% 
  filter(binary == "FAIL")
```

__12. What are the null and alternative hypotheses for this test? (Hint: we are testing the difference between two means, i.e. whether or not the population means are actually different between movies that pass the Bechdel tests and movies that do not pass)__
<!-- Your response here -->


Now we will use `t.test()` to run this whole hypothesis test with one line of code. 

To use this function for a two-way t-test:
* the first arg is `x`, the first set of data 
* the second is `y`, the data to compare with the first 
* third is the `alternative` arg, where we supply the alternative hypothesis (hint: either "two-sided", "greater", or "less")
* finally, `mu` is the true value of the mean (hint: we are testing the difference, which means if the means are equal, this will be 0)

__13. Run the `t.test()` in the code chunk below.__

```{r}

```

__14. What are your p-value and t-stat?__
<!-- Your response here -->


__15. What are your conclusions (reject or fail to reject)? Why?__
<!-- Your response here -->


### Conclusions

__16. Please write a short description of your group's experience working through this lab. What went well? What was difficult? Do you have any further questions or need for clarification (about either the statistics or R code)?__
<!-- Your response here -->


Acknowledgments: I used the "One sample T-tests" page on [cran.r-project.org](https://cran.r-project.org/web/packages/distributions3/vignettes/one-sample-t-test.html) for reference on conducting t-tests in R. The data are from fivethirtyeight and can be found on [their GitHub page](https://github.com/fivethirtyeight).
